Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-03-21 analysis/paper/shceof.Rmd
Pone referencias dinámicas a las "In Section 1..."

In Section 2 we describe the methods.
In Section 3.1, we analyse the spatial patterns of each complex EOF.
In Section 3.2 we study the spatial regressions with geopotential height and temperature anomalies.
In Section 3.3, we analyse the relationship between cEOF1 and Ozone, and between cEOF2 with the SAM and the PSA.
In Section 3.4 we study tropical forcings that explain the variability of each cEOF.
Finally, in Section 3.5 we show the relationship between these modes of variability and precipitation anomalies in South America and Oceania.

>>>>

In Section \@ref(methods) we describe the methods.
In Section \@ref(spatial) we analyse the spatial patterns of each complex EOF.
In Section \@ref(regressions) we study the spatial regressions with geopotential height and temperature anomalies.
In Section \@ref(other-variables) we analyse the relationship between cEOF1 and Ozone, and between cEOF2 with the SAM and the PSA.
In Section \@ref(tropical) we study tropical forcings that explain the variability of each cEOF.
Finally, in Section \@ref(precipitation) we show the relationship between these modes of variability and precipitation anomalies in South America and Oceania.
